Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-20 ms.tex
Bandara begone.

Figure~\ref{fig:miller} shows our predicted ${\rm L_{X}/L_{edd}}$ for
core (blue) and cusp (green) galaxies superimposed with x-ray
measurements (red stars), upper limits (red triangles) from
\citet{Miller+15}.  For our theoretical predictions $L_X=\epsilon
\Mdot c^2$, where $\epsilon$ is and efficiency factor and $\Mdot$ is
calculated using Equation~\eqref{eq:mdot_analytic}, with the value of
the wind heating parameter, $\vw$, and the mass return parameter,
$\eta$ set by the average star formation history for each $\Mbh$ (see
the black lines in Figures~\ref{fig:vwSource} and~\ref{fig:eta}). We
try two different prescriptions for $\epsilon$: 
$\epsilon=10^{-4}$ in the left-hand panel and $\epsilon=10^{-1}
\Mdot/0.01 \MdotEdd$ right-hand panel.

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{edd}$ predicted
  from our models compared to $L_X/L_{Edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}, with the wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
  the the average star formation histories in
  \citet{MosterNaab+:2013a} (the black lines in
  Figures~\ref{fig:vwSources} and~\ref{fig:eta}). Note that the star
  formation histories in \citet{MosterNaab+:2013a} are in terms of
  halo mass and for each $\Mbh$ we assign the halo mass, whose star
  formation history would produce a bulge consistent with the
  $\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.
  We also show upper limits $\epsilon_X \Mdot c^2/L_{edd}$ from
  thermal stability (purple) and Ia supernovae (orange).}
\end{figure*}

>>>>

Figure~\ref{fig:miller} shows our predicted ${\rm L_{X}/L_{edd}}$ for
core (blue) and cusp (green) galaxies superimposed with x-ray
measurements (red stars), upper limits (red triangles) from
\citet{Miller+15}.  For our theoretical predictions $L_X=\epsilon
\Mdot c^2$, where $\epsilon$ is and efficiency factor and $\Mdot$ is
calculated using Equation~\eqref{eq:mdot_analytic}, with the value of
the wind heating parameter, $\vw$, and the mass return parameter,
$\eta$ set by the average star formation history for each $\Mbh$ (see
the black lines in Figures~\ref{fig:vwSources} and~\ref{fig:eta}). We
try two different prescriptions for $\epsilon$: 
$\epsilon=10^{-4}$ in the left-hand panel and $\epsilon=10^{-1}
\Mdot/0.01 \MdotEdd$ right-hand panel.

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{edd}$ predicted
  from our models compared to $L_X/L_{Edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}, with the wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
  the the average star formation histories in
  \citet{MosterNaab+:2013a} (the black lines in
  Figures~\ref{fig:vwSources} and~\ref{fig:eta}--see
  Appendix~\ref{windheat} for a detailed description)).
  We also show upper limits $\epsilon_X \Mdot c^2/L_{\rm edd}$ from
  thermal stability (purple) and Ia supernovae (orange).}
\end{figure*}

### 2015-02-20 windheat.tex
Bandara begone.

We estimate the stellar wind heating provided by the {\it average} star formation history of galaxies of a given mass using the results of \citet{MosterNaab+:2013a} (their eqs.~[17]-[20]) and the $M_{\bullet}-M_{\rm
  halo}$ relation from \citet{BandaraCrampton+:2009a}.  Figure \ref{NickPlot2} shows the resulting $v_{\rm W}$ as a function of SMBH mass.  For comparison we also show cases in which the star formation rate is modulated sinuisoidally from its average value.   It seems that ``bumpy'' SF histories severely diminish $v_{\rm w}$ if the timescale for SF variability is a factor of a few or more greater than the duration of high-velocity winds (either 10 or 40 Myr). {\bf AG: this plot still uses the old ad hoc vw
  prescription? If so it would need to be fixed. In any case, we still
  differ in detail on the vw from stars}.

>>>>

We estimate the stellar wind heating provided by the {\it average}
star formation history of galaxies of a given $\Mbh$ using the results
of \citet{MosterNaab+:2013a} (their eqs.~[17]-[20]).  Note that the
star formation histories in \citet{MosterNaab+:2013a} are in terms of
halo mass. For a given $\Mbh$ we assign the halo mass whose star
formation history would produce a bulge consistent with the
$\Mbh-M_{\rm bulge}$ relationship from \citet{McConnellMa:2013a}.

 % Figure \ref{NickPlot2} shows the resulting $v_{\rm W}$ as a function of SMBH mass.  For comparison we also show cases in which the star formation rate is modulated sinuisoidally from its average value.   It seems that ``bumpy'' SF histories severely diminish $v_{\rm w}$ if the timescale for SF variability is a factor of a few or more greater than the duration of high-velocity winds (either 10 or 40 Myr). {\bf AG: this plot still uses the old ad hoc vw
  % prescription? If so it would need to be fixed. In any case, we still
  % differ in detail on the vw from stars}.
